
%The simple beginnings of a latex meeting document

\documentstyle{article}

\begin{document}

\title{Web UI Team}
\author{Kyle M, Katie M, Garrett D, Aryn G.}
\date{October 6, 2011}
\maketitle


\section{Review of Goals}
	\subsection{Authentication}
	Get SQL injection prevention in place and working.\\Encypt MySQL username/password database.\\Fix the duplicate username issue. 
	\subsection{Account Settings}
	Create an edit user settings page and be able to edit the MySQL database through it, keeping SQL injection prevention in mind.
	\subsection{Play}
	Work with the Osmus project to try and learn how to implement our own jWebSockets and server-side javascript.
	\subsection{Design}
	Look into eventually implementing the basic mock-up design, Learn CSS for that.

\section{Accomplishments}
	\subsection{User Authentication}
		\subsubsection{MySQL}
		A javascript version of SQL verification is in place, but that can be easily worked around be turning off javascript... Works for our purposes for the time being.
		\subsubsection{Account}
                      A new page for debugging purposes was made that prints out all the content in the database.\\User can now go to a user account settings page to edit there current information such as password, name, email, etc. 
	\subsection{Play}
	The Osmus project has been striped to bare-bones and being rebuilt as our own creation. User can visit web page and server and client can communicate through the Socket.
	\subsection{Design}
	We now have some CSS! Basic colors are in place. PHP style dropdown menus are in place and working for the most part.
	\subsection{content}
	More pages: Code of Conduct and Use of Terms.

\section{New Goals}
	\subsection{Play}
		Integrate original demo pong with the moving paddles into the current node and socket demo.
	\subsection{Style}
		Work more on the CSS for the site.\\More dropdown menu work.
	\subsection{MySQL}
		continue work on user account settings page.\\Figure out the duplicate username issue.
	
\section{Medium Term Goals}
	-Chat/Forum abilities.\\
	-Transition for clientside javescript SQL protection to serverside PHP, or Perl, etc. protection.
\section{Long Term Goals}
	-Need to create a PHP header (something that will be consistent on every PHP page).\\
	-Pure CSS menu system if that many menus are needed.\\
	-Create a scoring system for the animation.\\
	-Fancy Pong game in background of game.\\
	-Pretty W3C HTML/CSS validation icons.\\



\end{document}
