\documentclass{beamer}
\usepackage[latin1]{inputenc}
\usetheme{Warsaw}
\usecolortheme{dove}
\title[]{Server Group -- Week 2 Report}
\author{Daniel Guilak \\ Shelby Lee, Ryan Wheeler, Patrick Green}
\institute{Vir-Pong}
\date{23 Sep 2011}
\begin{document}

\begin{frame}
\titlepage
\end{frame}

\section{Progress}
\begin{frame}
\frametitle{Progress}
	\begin{itemize}[<+->]
		\item Everyone on-board with Github.
		\item Decided on a specification for server-client communication (WebSocket)
		\item Have two different implementations of the specification working.
		\begin{itemize}
			\item jWebSocket
			\item node.js
		\end{itemize}
		\item Web team should be set up with MySQL database and server access.
		
	\end{itemize}
\end{frame}

\subsection{WebSocket Overview}
\begin{frame}[WebSocket Overview]
\frametitle{WebSocket Overview}
	\begin{itemize}[<+->]
		\item What is WebSocket?
		\begin{itemize}
			\item Brand spankin' new
			\item Full-duplex, bi-directional communication with client/server over a single socket.
			\item Makes bi-directional web communication simpler.
		\end{itemize}
		\item Caveats
		\begin{itemize}
			\item Brand spankin' new.
			\item May need a small Java plugin for Android.
		\end{itemize}
	\end{itemize}
\end{frame}

\section{What We Need}
\begin{frame}[Needs]
	\frametitle{Needs}
	\begin{itemize}[<+->]
		\item Communication.
		\item Be willing to test.
	\end{itemize}
\end{frame}


\begin{frame}
\frametitle{What We're Working On}
\begin{itemize}[<+->]
	\item Java v. JavaScript
	\item Database Access
	\item Class/method definitions
\end{itemize}
\end{frame}
\end{document}
