\documentclass[12pt]{article}

% useful for formatting (align*, etc.) and for certain symbols (the QED box, etc.)
\usepackage{amsmath, amssymb, amsthm}

% for including graphics
\usepackage{graphicx}

% for conveniently specifying the spacing (\singlespacing, \doublespacing,
%    \onehalfspacing, etc.)
\usepackage{setspace}
\singlespacing

% this does some sort of symbol stuff
\usepackage{textcomp}

% A package for conveniently adjusting headers and such
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0 pt}
\rhead{\textit{\thepage}}
\cfoot{}

% Differently spaced itemize
\newenvironment{itemize*}%
  {\begin{itemize}%
  	\setlength{\parsep}{0pt}
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}

% Set the margins
\usepackage[top=1.8cm, bottom=1.8cm, left=1.8cm, right=1.8cm]{geometry}
% set up a new command to insert a little bit of vertical space
% (use this BEFORE a line break)
\newcommand{\padding}{\vspace*{.5cm}}

% set up an environment to format each hw problem in
\newenvironment{problem}[1]{\noindent\textbf{#1.}}{\vspace*{.5cm}}

\newenvironment{proof*}{\par\noindent{\bf Proof}\quad}
               {\quad\vrule height 8pt depth 0pt width 8pt\medskip\par}


\begin{document}
\thispagestyle{empty}
\begin{flushleft}
\singlespacing
Team: Server System Testing\\
Members Present: Jordan Apele,\\
Joey Lange*,\\
Garrett Dieckmann,\\
Kyle Monet,\\
Kyle Wenholz\\
Date: 11-1-2011 and 11-3-2011\\
*excused but not present on 11-1-2011
\end{flushleft}
\pagestyle{fancy}
\textbf{Review of Goals:}\\
\begin{itemize*}
\item Tasked with generating an initial plan for testing.
\item Familiarize selves with intermediate report.
\item Initialize the server.
\end{itemize*}

\textbf{Accomplishments:}\\
\begin{itemize*}
\item Kyle W. is trying to set up server. Having issues because the instructions don't discuss compilation of server software.  
\item After looking at the code submitted, we determined that our main focus will be the $server.js$ file.  
\item All team members have agreed to brief meetings after every class period and periodic large group sessions.
\item The next planned meeting is scheduled for Sunday, November 6, 2011.
\begin{itemize*}
\item The following use cases (found in the intermediate report) were divided up for test case creation:
\item Client connection (generic) - Kyle M.
\item Client connection (opening game) - Josef
\item Store Player Information - **
\item Update Scores - Jordan
\item Access Replay - **
\item Complete a Game - Garrett
\item AI Opponent - **
\end{itemize*}
\end{itemize*}
** Items that don't seem complete or in a state prepared for testing.\\

\textbf{New Goals:}\\
\begin{itemize*}
\item Wrap up installation of the server components. (Due 11-4-2011: Kyle W.)
\item Generate test cases out of assigned use cases. (Due 11-6-2011: All - Kyle W.)
\item Conceptualize a file or class structure for testing client interaction with the server. (Due 11-6-2011: All)
\item Review the style guide and begin comparing its rules with the actual code. (Due 11-6-2011: All)
\end{itemize*}



\end{document}
