%%%%%%%%%%%%%%%
% This file is concerned with testing and verification,
% a subsection of the implementation section.
%
% Please remember to compile the document from "00_finalreport.tex".
% It will not work otherwise.
%%%%%%%%%%%%%%%

	\subsection{Testing and Verification}
		The testing and verification for the VirPong website will be through validators and various kinds of testing. All the HTML and CSS code will be ran through the W3C validators available online. They will check for the indicated doctype syntax compliance of all of our scripts and compare them against the XHTML 1.1 standard. For all other types of scripts we will be using Google’s developer tools in Google Chrome to see resource load times and any errors thrown by the scripts.

We plan on performing four types of testing upon our code: unit, integration, system, and regression. For the unit testing we are going to use a program called QUnit. We will then uses integration testing across multiple departments of code. Then we will do some system testing against all of our requirements. In this stage of testing we will test scripts in the latest versions of Microsoft’s Internet Explorer, Mozilla’s Firefox, Apple’s Safari, and Google’s Chrome on a Windows 7 machine and a Ubuntu distribution of Linux. We will also report on each functionalities success on each platform and browser to report to the user. Lastly we will perform regression testing when we make additional releases of the software to make sure they implement all functions.
