
\documentclass[12pt]{article}

\usepackage{hyperref}

% useful for formatting (align*, etc.) and for certain symbols (the QED box, etc.)
\usepackage{amsmath, amssymb, amsthm}

% for including graphics
\usepackage{graphicx}

% for conveniently specifying the spacing (\singlespacing, \doublespacing,
% \onehalfspacing, etc.)
\usepackage{setspace}
\onehalfspacing

% this does some sort of symbol stuff
\usepackage{textcomp}

% A package for conveniently adjusting headers and such
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0 pt}
\rhead{\textit{\thepage}}
\cfoot{}

\usepackage{hyperref}

% Set the margins
\usepackage[top=1.8cm, bottom=1.8cm, left=1.8cm, right=1.8cm]{geometry}

% Differently spaced itemize
\newenvironment{itemize*}%
{\begin{itemize}%
    \setlength{\parsep}{0pt}
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
{\end{itemize}}
\newenvironment{enumerate*}%
{\begin{enumerate}%
    \setlength{\parsep}{0pt}
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
{\end{enumerate}}


% set up a new command to insert a little bit of vertical space
% (use this BEFORE a line break)
\newcommand{\padding}{\vspace*{.5cm}}

% set up an environment to format each hw problem in
\newenvironment{problem}[1]{\noindent\textbf{#1.}}{\vspace*{.5cm}}

\newenvironment{proof*}{\par\noindent{\bf Proof}\quad}
             {\quad\vrule height 8pt depth 0pt width 8pt\medskip\par}




\begin{document}
\thispagestyle{plain}
\begin{flushleft}
\singlespacing
Team: Server System Testing\\
Members Present: Jordan Apele,\\
Joey Lange*,\\
Garrett Dieckmann,\\
Kyle Monet,\\
Kyle Wenholz\\
Date(s): 11-6-2011 and 11-10-2011\\
*excused but not present on 11-6 and 11-10
\end{flushleft}
\pagestyle{fancy}
\section*{Review of Goals:}
\begin{itemize*}
\item Wrap up installation of the server components. (Due 11-4-2011: Kyle W.)
\item Generate test cases out of assigned use cases. (Due 11-6-2011: All minus Kyle W.)
\item Conceptualize a file or class structure for testing client interaction with the server. (Due 11-6-2011: All)
\item Review the style guide and begin comparing its rules with the actual code. (Due 11-6-2011: All)
\item Complete (finalize, Tex, and run) all test cases.  (Due 11-9-2011: All)
\end{itemize*}

\section*{Accomplishments:}
\begin{itemize*}
\item Kyle W. finished server installation on time.  Garrett even installed the server on his own system as a test.
\item All team members accomplished test case generation on time.
\item All team members completed conceptualization.
\item All testing was complete as of 11-9-2011.
\item Final defect reports and Tex submissions were made on 11-10-2011.
\item The Server System Testing team finalized all goals on 11-10-2011.
\end{itemize*}

\section*{New Goals:}
\begin{itemize*}
\item Await further instructions from Doctor Sawin.
\item Prepare for team re-assembly.
\end{itemize*}





\end{document}